ScipionBox: automatic processing for

### 2017-07-24 scipionbox.tex
Updates from ShareLaTeX
before start meassure results
previous to facility meeting

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage[T1]{fontenc}
\usepackage[table]{xcolor} % Colors and tables
\usepackage{color, colortbl} % Define new colors and use in tables
\usepackage{setspace} % Set paragraph lines space
%\usepackage{tabu} % Other table package
\usepackage{url} % Other table package
\usepackage{listings}
\usepackage{rotating}
\usepackage[strict]{changepage}
\usepackage[caption=false]{subfig}
\usepackage{fancyhdr}
\usepackage{rotating}
\usepackage{xr}
\usepackage{xspace}
%\externaldocument[Supp-]{supplementary_material}

@@

\lyxaddress{{\small \vspace{-0.5cm}$^{(a)}$Escuela Polit\'{e}cnica Superior, Universidad Aut\'{o}noma de Madrid, 28049 Cantoblanco, Madrid, Spain.}}
\lyxaddress{{\small$^{(b)}$ The National Resource for Automated Molecular Microscopy, The Scripps Research Institute, La Jolla, CA 92037, USA}}
\lyxaddress{{\small$^{(c)}$ Baylor College of Medicine, Houston, Texas 77030, USA}}
\lyxaddress{{\small$^{(d)}$ Lawrence Berkeley National Laboratory, Berkeley, CA 94720, USA}}
\lyxaddress{{\small$^{(e)}$ Howard Hughes Medical Institute, Columbia University, NY 10032, USA}}
\lyxaddress{{\small$^{(f)}$ Purdue University, Biological Sciences, IN 47907-2054, USA}}
\lyxaddress{{\small$^{(g)}$ Biocomputing Unit, National Center for Biotechnology (CSIC), C/ Darwin, 3, Campus Universidad Aut\'{o}noma, 28049 Cantoblanco,
Madrid, Spain.}}
\lyxaddress{{\small$^{(h)}$ Biozentrum, University of Basel, CH - 4058 Basel, Switzerland}}
\lyxaddress{{\small$^{(i)}$ MRC-LMB, Cambridge CB2 0QH, UK. 01223 267000, United Kingdom}}
\lyxaddress{{\small$^{(j)}$IMPMC, Sorbonne Universit\'{e}s - CNRS UMR 7590, UPMC Univ Paris 6, MNHN, IRD UMR 206, 75005 Paris, France.}} 
\lyxaddress{{\small$^{(k)}$Roosevelt University, Department of Biological, Chemical, and Physical Sciences, 1400 N. Roosevelt Blvd., Schaumburg, IL 60173, USA.}}
\lyxaddress{{\small$^{(l)}$Laboratory of Structural Biology Research, National Institute of Arthritis, Musculoskeletal and Skin Diseases,
National Institutes of Health, Bethesda, MD 20892, USA}}
\lyxaddress{{\small$^{(m)}$Massachusetts Institute of Technology, USA}}
%\lyxaddress{{\small$^{(14)}$Massachusetts Institute of Technology, USA}}
% 
% \lyxaddress{{\small \vspace{-0.5cm}$^{(3)}$Bioengineering Lab., Universidad CEU San Pablo, Campus Urb.
% Montepríncipe s/n, 28668 Boadilla del Monte, Madrid, Spain.}}
%

>>>>

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage[T1]{fontenc}
\usepackage[table]{xcolor} % Colors and tables
\usepackage{color, colortbl} % Define new colors and use in tables
\usepackage{setspace} % Set paragraph lines space
%\usepackage{tabu} % Other table package
\usepackage{url} % Other table package
\usepackage{listings}
\usepackage{rotating}
\usepackage[strict]{changepage}
\usepackage[caption=false]{subfig}
\usepackage{fancyhdr}
\usepackage{rotating}
\usepackage{xr}
\usepackage{xspace}
\usepackage{listings}

%\externaldocument[Supp-]{supplementary_material}

@@

%\lyxaddress{{\small \vspace{-0.5cm}$^{(a)}$Escuela Polit\'{e}cnica Superior, Universidad Aut\'{o}noma de Madrid, 28049 Cantoblanco, Madrid, Spain.}}
%\lyxaddress{{\small$^{(g)}$ Biocomputing Unit, National Center for Biotechnology (CSIC), C/ Darwin, 3, Campus Universidad Aut\'{o}noma, 28049 Cantoblanco,
%Madrid, Spain.}}
